Energy Regulation for Biologically-inspired Robotics

### 2021-09-17 latex/nserc/contributions.tex
Edited Part III

Over the course of my career, I have enjoyed several extracurricular roles which
developed my communication, interpersonal, and leadership skills.
What follows is a brief description of some of these roles, along with a summary
of what I learned.
\begin{itemize}
\item \textbf{Lionel Massey Fund Co-chair, Massey College, September 2021 -- Present}.
    I am one of six co-chairs for the Lionel Massey Fund (LMF) -- the social
    committee for Massey College, a graduate college at the University of
    Toronto. Thus far I have dramatically improved my
    communication and leadership skills by managing 13 orientation events for
    150 members of the college. I have learned to explicitly communicate my needs
    with others, and to ask questions to understand their needs so we all succeed.

\item \textbf{Teaching Assistant, 2017 -- Present}.
    I have been a teaching assistant for 14 engineering courses in the past 5 years.
    Each course has taught me better teaching skills, along with new ways of
    making the material more engaging.
    I focus most on attaining high student participation, and I find
    commonalities between myself and students so they feel comfortable asking
    questions.

\item \textbf{Jiu-Jitsu Instructor, 2019 -- Present}. 
    I am an instructor at the University of Toronto Jiu-Jitsu club. I teach
    people martial arts while fostering a safe, friendly atmosphere that
    encourages learning through action.
    This role has refined my communication and interpersonal skills:
    it has taught me to create learning plans for my students;
    break down difficult concepts into manageable chunks; 
    and reward mistakes, because the best way to learn is to try, fail, and
    to always try again.

\item \textbf{Science Payload Designer, Queen’s University Satellite Design
    Team, 2017 -- 2018}. 
    In this role, I taught C++ and information theory to the team’s software
    developers. I also learned project management skills, because I organized
    the satellite codebase but took on a supportive role for my peers (rather
    than writing the software myself).

\item \textbf{Head Programming Mentor, FIRST Team 2809, 2013 -- 2015}. 
    I mentored high school students in Object Oriented programming for robotics
    software. Together we programmed a robot in under 6 weeks and placed 3rd at
    the Ontario provincial competition in 2014.
    In this role I learned to give my students agency over the project, and to
    communicate with people from all over the world in high-stress situations.

>>>>

Over the course of my career, I have enjoyed several extracurricular roles which
developed my communication, interpersonal, and leadership skills.
What follows is a brief description of some of these roles, along with a summary
of what I learned.
\begin{itemize}
\item \textbf{Lionel Massey Fund Co-chair, Massey College, September 2021 -- Present}.
    I am one of six co-chairs for the Lionel Massey Fund (LMF) -- the social
    committee for Massey College, a graduate residence at the University of
    Toronto.
    In managing 13 orientation events for 150 members of the college, I have
    learned to explicitly communicate my needs with others, and to ask pointed
    questions to understand their needs.

\item \textbf{Teaching Assistant, 2017 -- Present}.
    I have been a teaching assistant for 14 engineering courses in the past 5 years.
    Each course I teach improves my communication skills, and I've learned
    many ways of making course material fun and engaging.
    I focus most on student participation by finding making them feel
    comfortable asking questions.

\item \textbf{Jiu-Jitsu Instructor, 2019 -- Present}. 
    I am an instructor at the University of Toronto Jiu-Jitsu club. I teach
    people martial arts while fostering a safe, friendly atmosphere that
    encourages learning through action.
    This role has refined my communication and interpersonal skills:
    it has taught me to create learning plans for my students;
    break down difficult concepts into manageable chunks; 
    and to reward mistakes, because the best way to learn is to try, fail, and
    always try again.

\item \textbf{Science Payload Designer, Queen’s University Satellite Design
    Team, 2017 -- 2018}. 
    In this role, I taught C++ and information theory to the team’s software
    developers. I learned project management skills by organizing
    the satellite codebase, and I took on a supportive role for my peers rather
    than writing the software myself.

\item \textbf{Head Programming Mentor, FIRST Team 2809, 2013 -- 2015}. 
    I mentored high school students in Object Oriented programming for robotics
    software. Together we programmed a robot in under 6 weeks and placed 3rd at
    the Ontario provincial competition in 2014.
    In this role I learned to lead my students by giving them agency over the
    project, and to communicate with people from all over the world in
    high-stress situations.
